---
title: "R Notebook"
output: html_notebook
---
```{r}
library(RColorBrewer)
library(stringr)
library(tidyr)
library(dplyr)
library(ggplot2)
install.packages("treemapify")
install.packages('fastDummies')
library(fastDummies)
library(treemapify)

```

```{r}

data = read.csv("C:/Users/mac/Desktop/WQD7001/group/Skincare Survey In Malaysia 2021.csv")

vis_cols = c("Gender.","Age.","Race.","Occupation.","Which..if.any..of.the.following.statements.applies.to.you.",
             "Which.of.the.following.types.of.ingredients.would.make.you.more.likely.to.buy.a.skin.care.product.",
             "How.do.did.you.choose.your.products.",
             "On.average..how.much.do.you.spend.on.skincare.products.each.month.",
             "I.experienced.allergies.after.use.a.new.skincare.products...Eg...Rashness..acne..purging.etc.",
             "Do.share.your.skincare.goals.and.motivation.with.us.")

length(vis_cols)
```


```{r}
dataID = data.frame(unique(data$Timestamp))
dataID$RecID = seq.int(nrow(dataID)) 
dataID$RecID = paste("RcdID",dataID$RecID,sep="_", collapse=NULL)
colnames(dataID) = c("Timestamp","RecID")
FinalData = left_join(data, dataID, by ='Timestamp')

```

## Visulizaiton of Gender.
```{r}
Count_Gender = FinalData %>% group_by(Gender.)%>%summarise(count = n_distinct(RecID))
ggplot(data = Count_Gender, aes(x = Gender.,y = count)) + geom_bar(stat = 'identity')
```

## Visulizaiton of Age.

```{r}
Count_Age. = FinalData %>% group_by(Age.)%>%summarise(count = n_distinct(RecID))
ggplot(data = Count_Age., aes(x = Age.,y = count)) + geom_bar(stat = 'identity')
```


## Visulizaiton of Race.
```{r}

Count_Race. = FinalData %>% group_by(Race.)%>%summarise(count = n_distinct(RecID))
ggplot(data = Count_Race., aes(x = Race.,y = count)) + geom_bar(stat = 'identity')+theme(axis.text.x = element_text(angle = 90, hjust = 1))

```

## Visulizaiton of Occupation.

```{r}
Count_Occupation. = FinalData %>% group_by(Occupation.)%>%summarise(count = n_distinct(RecID))
ggplot(data = Count_Occupation., aes(x = Occupation.,y = count)) + geom_bar(stat = 'identity')
```

## Visulizaiton of Which..if.any..of.the.following.statements.applies.to.you.
```{r}
Count_Which..if.any..of.the.following.statements.applies.to.you. = FinalData %>% group_by(Which..if.any..of.the.following.statements.applies.to.you.)%>%summarise(count = n_distinct(RecID))
ggplot(data = Count_Which..if.any..of.the.following.statements.applies.to.you., aes(x = Which..if.any..of.the.following.statements.applies.to.you.,y = count)) + geom_bar(stat = 'identity')+theme(axis.text.x = element_text(angle = 90, hjust = 1))
```



## Visulizaiton of Which.of.the.following.types.of.ingredients.would.make.you.more.likely.to.buy.a.skin.care.product.
```{r}
Count_Which.of.the.following.types.of.ingredients.would.make.you.more.likely.to.buy.a.skin.care.product. = FinalData %>% group_by(Which.of.the.following.types.of.ingredients.would.make.you.more.likely.to.buy.a.skin.care.product.)%>%summarise(count = n_distinct(RecID))
ggplot(data = Count_Which.of.the.following.types.of.ingredients.would.make.you.more.likely.to.buy.a.skin.care.product., aes(x = Which.of.the.following.types.of.ingredients.would.make.you.more.likely.to.buy.a.skin.care.product.,y = count)) + geom_bar(stat = 'identity')+theme(axis.text.x = element_text(angle = 30, hjust = 1))

```


## The visulization of How.do.did.you.choose.your.products.
```{r}

Count_How.do.did.you.choose.your.products. = FinalData %>% group_by(How.do.did.you.choose.your.products.)%>%summarise(count = n_distinct(RecID))
ggplot(data = Count_How.do.did.you.choose.your.products., aes(x = How.do.did.you.choose.your.products.,y = count)) + geom_bar(stat = 'identity')+theme(axis.text.x = element_text(angle = 30, hjust = 1))

```



## The visulization of On.average..how.much.do.you.spend.on.skincare.products.each.month.
```{r}
Count_On.average..how.much.do.you.spend.on.skincare.products.each.month. = FinalData %>% group_by(On.average..how.much.do.you.spend.on.skincare.products.each.month.)%>%summarise(count = n_distinct(RecID))
ggplot(data = Count_On.average..how.much.do.you.spend.on.skincare.products.each.month., aes(x = On.average..how.much.do.you.spend.on.skincare.products.each.month.,y = count)) + geom_bar(stat = 'identity')+theme(axis.text.x = element_text(angle = 30, hjust = 1))
```



## The visulization of I.experienced.allergies.after.use.a.new.skincare.products...Eg...Rashness..acne..purging.etc.
```{r}
Count_I.experienced.allergies.after.use.a.new.skincare.products...Eg...Rashness..acne..purging.etc. = FinalData %>% group_by(I.experienced.allergies.after.use.a.new.skincare.products...Eg...Rashness..acne..purging.etc.)%>%summarise(count = n_distinct(RecID))
ggplot(data = Count_I.experienced.allergies.after.use.a.new.skincare.products...Eg...Rashness..acne..purging.etc., aes(x = I.experienced.allergies.after.use.a.new.skincare.products...Eg...Rashness..acne..purging.etc.,y = count)) + geom_bar(stat = 'identity')+theme(axis.text.x = element_text(angle = 0, hjust = 1))
```


## The visulization of Do.share.your.skincare.goals.and.motivation.with.us.

```{r}
Count_Do.share.your.skincare.goals.and.motivation.with.us. = FinalData %>% group_by(Do.share.your.skincare.goals.and.motivation.with.us.)%>%summarise(count = n_distinct(RecID))

ggplot(data = Count_Do.share.your.skincare.goals.and.motivation.with.us., aes(area = count,label = Do.share.your.skincare.goals.and.motivation.with.us.))+
 geom_treemap(fill="steelblue") +
 geom_treemap_text(fontface = "italic", colour = "red", place = "centre",grow = TRUE,alpha=.6)+
 scale_fill_distiller(palette="Greens")
```











## Random Forest Model Building
```{r}

FinalData = FinalData[complete.cases(FinalData), ]
FinalData = FinalData %>% filter(Age. != "")
Model_data <- subset (FinalData, select = -c (Timestamp,Do.share.your.skincare.goals.and.motivation.with.us.,RecID)) 



categorical_col_updated = c("Gender.","Age.","Race.","Occupation.","Have.you.ever.used.any.skin.care.products.","Which..if.any..of.the.following.statements.applies.to.you.","Which.of.the.following.types.of.ingredients.would.make.you.more.likely.to.buy.a.skin.care.product.","How.do.did.you.choose.your.products.","Do.you.use.samples.before.buying.skincare.products.","How.often.do.you.buy.skincare.products.","Where.do.you.purchase.your.skin.care.products.","Do.you.think.that.technology.can.improve.your.skincare.routine.","Do.you.have.heard.about.AI..Artificial.Intelligent..","After.you.know.about.AI..do.you.want.to.have.a.skin.scanning.app.that.can.customize.skincare.regime.")

Model_dataf <- dummy_cols(Model_data, select_columns = categorical_col_updated)
```


```{r}

Model_dataf <- subset (Model_dataf, select = -c(Gender.,Age.,Race.,Occupation.,Have.you.ever.used.any.skin.care.products.,Which..if.any..of.the.following.statements.applies.to.you.,Which.of.the.following.types.of.ingredients.would.make.you.more.likely.to.buy.a.skin.care.product.,How.do.did.you.choose.your.products.,Do.you.use.samples.before.buying.skincare.products.,How.often.do.you.buy.skincare.products.,Where.do.you.purchase.your.skin.care.products.,Do.you.think.that.technology.can.improve.your.skincare.routine.,Do.you.have.heard.about.AI..Artificial.Intelligent..,After.you.know.about.AI..do.you.want.to.have.a.skin.scanning.app.that.can.customize.skincare.regime.))

```


```{r}
library(dplyr)

Model_dataf <- Model_dataf %>% 
  mutate(On.average..how.much.do.you.spend.on.skincare.products.each.month. = case_when(On.average..how.much.do.you.spend.on.skincare.products.each.month. == "Less than RM 20"   ~ 1,
                           On.average..how.much.do.you.spend.on.skincare.products.each.month. == "RM 20 - RM 50"   ~ 2,
                           On.average..how.much.do.you.spend.on.skincare.products.each.month. == "RM 50 - RM 100" ~ 3, 
                           On.average..how.much.do.you.spend.on.skincare.products.each.month. == "RM 100 - RM 150" ~ 4,
                           On.average..how.much.do.you.spend.on.skincare.products.each.month. == "> RM 150" ~ 5
                           ))
```


```{r}
Model_dataf_X = subset (Model_dataf, select = -c(On.average..how.much.do.you.spend.on.skincare.products.each.month.))
colnames(Model_dataf_X) <- paste("Col",seq(1, length(colnames(Model_dataf_X))),sep="_", collapse=NULL)
Model_dataf_Y = data.frame(Model_dataf[,"On.average..how.much.do.you.spend.on.skincare.products.each.month."])
colnames(Model_dataf_Y) <- "Label"
Model_dataf = cbind(Model_dataf_X,Model_dataf_Y)
Model_dataf$Label = as.factor(Model_dataf$Label)

```



```{r}
library(caret)
set.seed(101)
split_val = createDataPartition(Model_dataf$Label, p = 0.80, list = FALSE) 
train_data = Model_dataf[split_val,]
test_data = Model_dataf[-split_val,]
```


```{r}
###MODELLING OF DATA USING MACHINE LEARNING ALGORITHMS####
#Defining error metrics to check the error rate and accuracy of the Regression ML algorithms
 
#1. MEAN ABSOLUTE PERCENTAGE ERROR (MAPE)
MAPE = function(y_actual,y_predict){
  mean(abs((y_actual-y_predict)/y_actual))*100
}
 
#2. R SQUARE error metric -- Coefficient of Determination
RSQUARE = function(y_actual,y_predict){
  cor(y_actual,y_predict)^2
}
```


```{r}
##MODEL 3: RANDOM FOREST
library(randomForest)
set.seed(123)



RF_model = randomForest(Label~., train_data, ntree = 300, importance = TRUE,proximity=TRUE)
RF_predict=predict(RF_model,subset(test_data, select = -c(Label)))


RF_model



```



```{r}
obs_p_ran = data.frame(prob=RF_predict,obs=test_data$Label)
obs_p_ran
```



```{r}
table(test_data$Label,RF_predict,dnn=c("True","predict"))
```


```{r}
#install.packages("pROC")
library(pROC)
ran_roc <- roc(test_data$Label,as.numeric(RF_predict))
plot(ran_roc, print.auc=TRUE, auc.polygon=TRUE, grid=c(0.1, 0.2),grid.col=c("green", "red"), max.auc.polygon=TRUE,auc.polygon.col="skyblue", print.thres=TRUE,main='ROC curve,mtry=3,ntree=500')

```












